Capstone Movielens Report

### 2025-12-11 reports/capstone-movielens.site/05.appendix.Rmd
Micro fix for function's description: `train_UMGY_SmoothedDay_effect.cv`.

This function is also called within other helper functions, such as the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) function (described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization] of *this Appendix*, respectively). The usage in the latter function is shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) section of *this Description* below.

>>>>

This function is also called within other helper functions, such as the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) (described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization] of *this Appendix*, respectively). The usage in the latter function is shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) section of *this Description* below.
